Smart Representations: {R}ationality and Evolution in a Richer Environment

### 2015-12-17 paper/paper.tex
sec com paper rewrite

Formally, given a class $\mathcal{G} $ of strategic games, the subjective representation scheme
for agent $i$ is a function $\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ that gives a
subjective preference $\theta \in \Theta$ and an epistemic state $e \in E$ for any game
$G \in \mathcal{G}$. A subjective preference $\theta$ for game $G$ and agent $i$ is just a
utility function for $G$. This can but need not be different from the actual payoff function of
$G$, which we interpret as the objective evolutionary fitness. An epistemic state $e$ for game
$G$ is some specification of a player's uncertainty about the co-players' behavior. Finally, an
action selection function for agent $i$ is a function
$\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
representation of the game $ (\theta,e) \in \Theta \times E$ with a set of prescribed actions
for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
readability in the following.

To keep matters simple the focus is on \emph{uniform}
and \emph{general} ways of forming preference and beliefs consistently across decision
situations.

We focus on two (\textit{subjective}) \emph{preference types} and two \emph{belief types}. We
view a preference type as a function $\tau: \mathcal{G} \rightarrow \Theta$, and a belief type
as a general disposition to form beliefs about the co-player’s behavior. The two possible
dispositions that we take account of are precise probabilistic belief and imprecise belief, as
we will explain in the next section. Since we are most interested here in studying whether
evolutionary pressure could support non-veridical subjective preferences, the two preference
types that we consider are: the veridical type $\tau^\pi$, who uses the actual payoff function
$\pi$ of the actual game $G$, and the regret type $\tau^{reg}$, who looks at the regret
transformation of the actual game $G$. Finally, the action selection function $\kappa$ that we
use in this paper is \textit{maxmin expected utility} \citep{gilsch89}, for reasons that will be clear
and justified in the following two sections.

>>>>

Formally, given a class of strategic games $\mathcal{G}$, the subjective representation scheme
for agent $i$ is a function $\gamma_i: \mathcal{G} \rightarrow \Theta \times E$ that gives a
subjective preference $\theta \in \Theta$ and an epistemic state $e \in E$ for any game
$G \in \mathcal{G}$. A subjective preference $\theta$ for $G$ and $i$ is just a utility
function for $G$. This can but need not be different from the actual payoff function of $G$. An
epistemic state $e$ for $G$ and $i$ is some specification of $i$'s uncertainty about the
co-players' behavior. Finally, an action selection function for agent $i$ is a function
$\kappa_i: \Theta \times E \rightarrow \pow{A_i} $, that associates any subjective
representation $\gamma_i(G) = (\theta,e)$ of $G$ with a set of prescribed actions
for $i$ in $G$ under $i$'s subjective representation of $G$. We drop the index $i$ for
readability in the following.

To keep matters simple the focus is on \emph{uniform} and \emph{general} ways of forming
preferences and beliefs consistently across decision situations. We consider two
\emph{preference types} and two \emph{belief types}: subjective preferences either coincide
with the actual, true payoffs or are given by the regret transformation of the actual game;
beliefs are either precise probabilistic beliefs modelled by a single probability distribution,
or they are imprecise probabilistic beliefs modelled by a set of probability distributions. The
action selection function $\kappa$ is fixed to \textit{maxmin expected utility}
\citep{gilsch89}, for reasons explained in the following.
